---
title: "Setting up your CV with datadrivencv"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{setting_up_your_cv}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(datadrivencv)
```

# Goal

This document will provide a small bit of context for the creation of the package and a sep-through of going from zero to html and pdf CV built from data. 

# Motivation 

## Updating a CV is not fun

Anytime I would go to add something to my CV I ended up wanting to change the format a tiny bit. This usually meant the entire word document completely falling apart and needing to have each entry copied and pasted into a new version.

Ultimately this process felt formulaic and repetitive, prime indicators they could be done better with code. Using a spreadsheet to store each entry in the CV and R to write markdown seemed like the way to go. Pagedown made this even easier. Meaning that the same CV could be rendered with interactive HTML and PDF without changing the underlying rendering engine like was done with kniting to pdf vs knitting to html. 

## No lock-in

Inspired heavily the the `usethis` package, `datadrivencv` strives to make itself unneccesary. The main function is `use_data_driven_cv`, which sets up the files you need to build your CV. These files are self-contained meaning if you uninstall `datadrivencv` your CV will still knit fine. All the R code logic is contained in a sourced script so if you want to change it you can do so. This is meant to be a jumping off point for you to build your own custom CV, you may at first want to leave it as is and then slowly tweak things to keep it fresh. You have all the code, so you can!

# Using it

The first step to using the package is the `use_data_driven_cv()` function. This function takes a few input parameters and when when run, sets up a series of files in your current working directory. E.g. 

```r
datadrivencv::use_datadriven_cv(
  full_name = "Nick Strayer",
  data_location = "https://docs.google.com/spreadsheets/d/14MQICF2F8-vf8CKPF1m4lyGKO6_thG-4aSwat1e2TWc",
  pdf_location = "https://github.com/nstrayer/cv/raw/master/strayer_cv.pdf",
  html_location = "nickstrayer.me/cv/",
  source_location = "https://github.com/nstrayer/cv"
)
```

This code is all that's needed to setup my full CV. It outputs four files: 

### `cv.Rmd` 
An RMarkdown file with various sections filled in. Edit this to fit your personal needs. 

### `dd_cv.css`
A custom set of CSS styles that build on the default `Pagedown` "resume" template. Again, edit these as desired.

### `render_cv.R`
Use this script to build your CV in both PDF and HTML at the same time. 

### `CV_Printer_Class.R`
A R6 class and helper functions that performs the dirty work making the HTML output work for PDF printing. E.g. Replacing markdown links with superscripts and a links section, tweaking the CSS to account for chrome printing quirks, etc..




